### 2020-08-25 code/figureSM2.Rmd
Fix figureSM2 code chunk

```
{r SM2}

@@

sampsum = summary(samps)
sampsum

@@

mortpl <- ggplot(menmort) + 
    geom_line(aes(yrnum,nsurv/100000),col="blue",data=menmort) +
    geom_line(aes(yrnum,nsurv/100000),col="red",data=wommort)+
    stat_function(fun=function(x) mccdf(x),col="green")+
    stat_function(fun=function(x) fccdf(x),col="orange")+labs(title="1-cdf(age) for Men and Women (CDC Data vs  model fit)",x="Age (yrs)",y="1-cdf") +
    theme_minimal()

print(mortpl)

```

>>>>

```{r SM2}
## mortality data from CDC:
namesmort = c("agerng","pdead","nsurv","ndie","pyrs","pyrsabove","expectedlife")
menmort = read_csv("../data/survival/lifetables/Table02.csv",skip=2)
## drop the final row, it's just a text info statement
menmort = menmort[1:NROW(menmort)-1,] 
wommort = read_csv("../data/survival/lifetables/Table03.csv",skip=2)
wommort = wommort[1:NROW(wommort)-1,]

names(menmort) = namesmort
names(wommort) = namesmort
yrs=seq(0,100,by=1);
menmort$yrnum = yrs
wommort$yrnum = yrs

@@

sampsum = summary(samps)

@@

mortpl <- ggplot(menmort) + 
    geom_line(aes(yrnum,nsurv/100000),col="#0072B2",data=menmort) +
    geom_line(aes(yrnum,nsurv/100000),col="#D55E00",data=wommort)+
    stat_function(fun=function(x) mccdf(x),col="#009E73")+
    stat_function(fun=function(x) fccdf(x),col="#E69F00")+labs(title="1-cdf(age) for Men and Women (CDC Data vs  model fit)",x="Age (yrs)",y="1-cdf") +
    theme_minimal()

print(mortpl)
```
